---
title: "Lab 1 Homework"
author: "Karen Kyutoku"
date: "2022/1/4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**1. Please complete the [class survey](https://forms.gle/hh5hmzTZgLYxkP7W9) if you have not already done so.**

**2. What is the difference between R and RStudio? What is GitHub and why is it useful to programmers?** 
R is a software and a language that programmers use in RStudio, a free software which develops an environment for R programming for scientific research. 
GitHub is a development platform and an open source which allows people to collaborate and work on their projects.It can also manage repository efficiently.

**3. Navigate to my [BIS15L](https://github.com/jmledford3115/BIS15LW2022_jledford) repository on GitHub. Notice that near the bottom there is a nice, clean description of the repository. You want this on your repository! It is built by making edits to the `README.md` file using the RMarkdown conventions. Edit your repository's `README.md` file so that you have a clean informative description, including your email address. Be creative! You don't need to just copy mine. There are lots of examples online.**  

**4. Calculate the following expressions. Be sure to include each one in a separate code chunk.**  
```{r}
+5-3*2
```
```{r}
+8/2**2
```
**5. Did any of the results in #4 surprise you? Write two programs that calculate each expression such that the result for the first example is 4 and the second example is 16.**    
```{r}
+10-3*2
```
```{r}
+2*4+8
```
**6. `Objects` in R are a way in which we can store data or operations. We will talk more about objects next week. For now, make a new object `pi` as 3.14159265359 by running the following code chunk. You should now see the object `pi` in the environment window in the top right.**
```{r}
pi <- 3.14159265359
```

**7. Let's say we want to multiply `pi` by 2. Using the same arithmetic principles that we just learned, write a code chunk that performs this operation using the object we created.**  
```{r}
pi*2
```

**8. In order to get help with any command in R, just type a `?` in front the command of interest. Practice this by running the following code chunk.**  
```{r}
?mean
```

**9. Let's calculate the mean for the numbers 2, 8, 6, 4, 9, 10. I have built an object `x` for you below so all you need to do is run the first code chunk and then create a second code chunk that shows the calculation. Give it a try!**  
```{r}
x <- c(2, 8, 6, 6, 7, 4, 9, 9, 9, 10)
```
```{r}
mean(x)
```

**10. Repeat the procedure above, but this time calculate the median.**  
```{r}
median(x)
```

